---
title: "best-fit PRS and plot results"
author: "Mary T. Yohannes"
date: "10/13/2021"
output: html_document
---

# load needed libs 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(data.table)
library(plotly)
library(gridExtra)
library(fmsb)
```

# PLINK PRS plots

# MULTIPLE SAMPLES all at once 

# Plot I - find the "best-fit" PRS and plot (non-linear regression)
```{r}
# dataset names
sample_names <- c("celso", "cgs1c", "gawli", "xclm2", "xswe1", "xclo3", "xswe6", "xswe5") 

# pval thresholds 
p.threshold <- c(0.001,0.05,0.1,0.2,0.3,0.4,0.5) 

# for each dataset 
for (name in sample_names){
  # read pheno table - already produced with qc files 
  phenotype <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".pheno"), header=T)

  # read pc table 
  pcs <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".eigenvec"), header=F)

  # rename pc table columns
  colnames(pcs) <- c("FID", "IID", paste0("PC",1:6))

  # read sex table 
  covariate <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".cov"), header=T)

  # merge the 3 tables that were read above
  pheno <- merge(merge(phenotype, covariate, by=c("FID", "IID")), pcs, by=c("FID","IID")) 

  # run glm for binomial regression 
  null.model <- glm(as.factor(PHENOTYPE)~., data=pheno[,!colnames(pheno)%in%c("FID","IID")], family='binomial') 
  
  # summary of model to compute p-values
  null.model.summary <- summary(null.model)

  # obtain the Nagelkerke's (pseudo) R^2 for the null model
  null.r2 <- NagelkerkeR2(null.model)$R2  

  # to hold final result 
  prs.result <- NULL 

  # set up function to find best-fit PRS 
  for(i in p.threshold){
    # merge the merged table (pheno) with the SCORE column of a new table
    pheno.prs <- merge(pheno, read.table(paste0("~/Desktop/Broad/tj/prs/batch_outputs/mdd_updated/", name, "/", name, ".", i, ".profile"), header=T)[,c("FID","IID", "SCORE")], by=c("FID", "IID"))
    
    # run glm binomial with the new merged dataset that has an additional SCORE column
  	model <- glm(as.factor(PHENOTYPE)~., data=pheno.prs[,!colnames(pheno.prs)%in%c("FID","IID")], family='binomial') 
  	
  	# summary of model to compute p-values
    model.summary <- summary(model)
  	
  	# obtain the Nagelkerke's (pseudo) R^2
  	model.r2 <- NagelkerkeR2(model)$R2  
  	
  	# find the difference between the two R^2 values
  	prs.r2 <- model.r2-null.r2  
  	
  	# obtain the coefficients for the SCORE row
  	prs.coef <- model.summary$coeff["SCORE",]   
  	
  	# set up final result table 
  	prs.result <- rbind(prs.result, data.frame(Threshold=i, R2=prs.r2, P=as.numeric(prs.coef[4]), BETA=as.numeric(prs.coef[1]), SE=as.numeric(prs.coef[2]))) 
  } 
  
  # which is the best-fit PRS?
  print(prs.result[which.max(prs.result$R2),]) 
  
  # generate a pretty format for p-value output
  prs.result$print.p <- round(prs.result$P, digits = 3)
  prs.result$print.p[!is.na(prs.result$print.p) & prs.result$print.p == 0] <- format(prs.result$P[!is.na(prs.result$print.p) & prs.result$print.p == 0], digits = 2)
  prs.result$print.p <- sub("e", "*x*10^", prs.result$print.p)

  # initialize ggplot, requiring the threshold as the x-axis (use factor so that it is uniformly distributed)
  ggplot(data = prs.result, aes(x = factor(Threshold), y = R2)) +
    
    # specify that we want to print p-value on top of the bars
    geom_text(
      aes(label = paste(print.p)),
      vjust = -1.5,
      hjust = 0,
      angle = 45,
      cex = 4,
      parse = T
    ) +
    
    # specify the range of the plot, *1.25 to provide enough space for the p-values
    scale_y_continuous(limits = c(0, max(prs.result$R2) * 1.25)) +
    
    # specify the axis labels
    xlab(expression(italic(P) - value ~ threshold ~ (italic(P)[T]))) +
    ylab(expression(paste("PRS model fit:  ", R ^ 2))) +
    
    # draw a bar plot
    geom_bar(aes(fill = -log10(P)), stat = "identity") +
    
    # specify the colors
    scale_fill_gradient2(
      low = "dodgerblue",
      high = "firebrick",
      mid = "dodgerblue",
      midpoint = 1e-4,
      name = bquote(atop(-log[10] ~ model, italic(P) - value),)
    ) +
    
    # add title
    labs(title=paste0(name, " (mdd - updated)")) +
    
    # some beautification of the plot
    theme_classic() + theme(
      axis.title = element_text(face = "bold", size = 18),
      axis.text = element_text(size = 14),
      legend.title = element_text(face = "bold", size =18),
      legend.text = element_text(size = 14), axis.text.x = element_text(angle = 45, hjust = 1)
    )

  # save plots - if you don't want to save the plots to a file and want to print them instead, add a print wrapper around ggplot and comment out this line ("print" prints the plots while in the for loop)
  ggsave(paste0("~/Desktop/Broad/tj/prs/plots/mdd_updated/", name, "_glm_bar_plot(mdd - updated).png"), height = 7, width = 7)
}  
```


# Plot II (A) - visualise the relationship between the "best-fit" PRS (which may have been obtained from any of the PRS programs) and the phenotype of interest, coloured according to sex
```{r}
# dataset names

# FOR BIP - 0.5 was the P-value threshold that generated the "best-fit" PRS except for cgs1c (0.3) and gawli (0.4) so run those two separately 
#sample_names <- c("celso", "xclm2", "xswe1", "xclo3", "xswe6", "xswe5") 

# FOR MDD - celso = 0.1, cgs1c = 0.5, gawli = 0.5, xclm2 = 0.2, xswe1 = 0.05, xclo3 = 0.4, xswe6 = 0.3, xswe5 = 0.5
sample_names <- c("cgs1c", "gawli", "xswe5") 

for (name in sample_names){
  # read in files
  prs <- read.table(paste0("~/Desktop/Broad/tj/prs/batch_outputs/mdd_updated/", name, "/", name, ".0.5.profile"), header=T) # 0.5 was the P-value threshold that generated the "best-fit" PRS for 3 samples 
  pheno <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".pheno"), header=T)
  sex <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".cov"), header=T)
  
  # rename the sex
  sex$Sex <- as.factor(sex$SEX)
  levels(sex$Sex) <- c("Male", "Female")
  
  # merge the files
  dat <- merge(merge(prs, pheno), sex)
  
  # start plotting
  print(ggplot(dat, aes(x=SCORE, y=PHENOTYPE, color=Sex))+
    geom_point()+
    theme_classic()+
    labs(title=paste0(name, " (mdd - updated)")) +
    labs(x="Polygenic Score", y="PHENOTYPE"))
  ggsave(paste0("~/Desktop/Broad/tj/prs/plots/mdd_updated/", name, "_scatter_plot(mdd - updated).png"), height = 7, width = 7) # remove print wrapper around ggplot before trying to save since "print" prints the plots while in the for loop
}
```

# Plot II (B) - generate plots for the ones with different P-value threshold that generated the "best-fit" PRS (not 0.5)
```{r}
# FOR BIP - cgs1c = 0.3 and gawli = 0.4 

# FOR MDD - celso = 0.1, xclm2 = 0.2, xswe1 = 0.05, xclo3 = 0.4, xswe6 = 0.3 - just rerun the following codes for each one by changing the profile file that's being read in

# dataset name
name1 = "xswe6"

# read in files
prs1 <- read.table(paste0("~/Desktop/Broad/tj/prs/batch_outputs/mdd_updated/", name1, "/", name1, ".0.3.profile"), header=T) # 0.3 was the P-value threshold that generated the "best-fit" PRS
pheno1 <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name1, "/scz.", name1, ".pheno"), header=T)
sex1 <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name1, "/scz.", name1, ".cov"), header=T)

# rename the sex
sex1$Sex <- as.factor(sex1$SEX)
levels(sex1$Sex) <- c("Male", "Female")
  
# merge the files
dat1 <- merge(merge(prs1, pheno1), sex1)

# start plotting
ggplot(dat1, aes(x=SCORE, y=PHENOTYPE, color=Sex))+
  geom_point()+
  theme_classic()+
  labs(title=paste0(name1, " (mdd - updated)")) +
  labs(x="Polygenic Score", y="PHENOTYPE")

ggsave(paste0("~/Desktop/Broad/tj/prs/plots/mdd_updated/", name1, "_scatter_plot(mdd - updated).png"), height = 7, width = 7)


# dataset name
name2 = "xclo3"

# read in files
prs2 <- read.table(paste0("~/Desktop/Broad/tj/prs/batch_outputs/mdd_updated/", name2, "/", name2, ".0.4.profile"), header=T) # 0.4 was the P-value threshold that generated the "best-fit" PRS
pheno2 <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name2, "/scz.", name2, ".pheno"), header=T)
sex2 <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name2, "/scz.", name2, ".cov"), header=T)

# rename the sex
sex2$Sex <- as.factor(sex2$SEX)
levels(sex2$Sex) <- c("Male", "Female")
  
# merge the files
dat2 <- merge(merge(prs2, pheno2), sex2)

# start plotting
ggplot(dat2, aes(x=SCORE, y=PHENOTYPE, color=Sex))+
  geom_point()+
  theme_classic()+
  labs(title=paste0(name2, " (mdd - updated)")) +
  labs(x="Polygenic Score", y="PHENOTYPE")

ggsave(paste0("~/Desktop/Broad/tj/prs/plots/mdd_updated/", name2, "_scatter_plot(mdd - updated).png"), height = 7, width = 7)
```

# ####################################################################

# #################################################################

# same to the above run but just for ONE SAMPLE

# Plot I - find the "best-fit" PRS and plot (non-linear regression)
```{r}
# pval thresholds 
p.threshold <- c(0.001,0.05,0.1,0.2,0.3,0.4,0.5) 


# read pheno table for one group  
name = "gawli"
phenotype <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".pheno"), header=T)

# read pc table 
pcs <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".eigenvec"), header=F)

# rename pc table columns
colnames(pcs) <- c("FID", "IID", paste0("PC",1:6))

  # read sex table 
covariate <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".cov"), header=T)

# merge the 3 tables that were read above
pheno <- merge(merge(phenotype, covariate, by=c("FID", "IID")), pcs, by=c("FID","IID")) 

# run glm for binomial regression 
null.model <- glm(as.factor(PHENOTYPE)~., data=pheno[,!colnames(pheno)%in%c("FID","IID")], family='binomial') 
  
# summary of model to compute p-values
null.model.summary <- summary(null.model)

# obtain the Nagelkerke's (pseudo) R^2 for the null model
null.r2 <- NagelkerkeR2(null.model)$R2  

# to hold final result 
prs.result <- NULL 

# set up function to find best-fit PRS 
for(i in p.threshold){
  # merge the merged table (pheno) with the SCORE column of a new table
  pheno.prs <- merge(pheno, read.table(paste0("~/Desktop/Broad/tj/prs/batch_outputs/mdd/", name, "/", name, ".", i, ".profile"), header=T)[,c("FID","IID", "SCORE")], by=c("FID", "IID"))
    
  # run glm binomial with the new merged dataset that has an additional SCORE column
  model <- glm(as.factor(PHENOTYPE)~., data=pheno.prs[,!colnames(pheno.prs)%in%c("FID","IID")], family='binomial') 
  	
  # summary of model to compute p-values
  model.summary <- summary(model)
  	
  # obtain the Nagelkerke's (pseudo) R^2
  model.r2 <- NagelkerkeR2(model)$R2  
  	
  # find the difference between the two R^2 values
  prs.r2 <- model.r2-null.r2  
  	
  # obtain the coefficients for the SCORE row
  prs.coef <- model.summary$coeff["SCORE",]   
  	
  # set up final result table 
  prs.result <- rbind(prs.result, data.frame(Threshold=i, R2=prs.r2, P=as.numeric(prs.coef[4]), BETA=as.numeric(prs.coef[1]), SE=as.numeric(prs.coef[2]))) 
} 
  
# which is the best-fit PRS?
print(prs.result[which.max(prs.result$R2),]) 
  
# generate a pretty format for p-value output
prs.result$print.p <- round(prs.result$P, digits = 3)
prs.result$print.p[!is.na(prs.result$print.p) & prs.result$print.p == 0] <- format(prs.result$P[!is.na(prs.result$print.p) & prs.result$print.p == 0], digits = 2)
prs.result$print.p <- sub("e", "*x*10^", prs.result$print.p)

# initialize ggplot, requiring the threshold as the x-axis (use factor so that it is uniformly distributed)
print(ggplot(data = prs.result, aes(x = factor(Threshold), y = R2)) +
    
    # specify that we want to print p-value on top of the bars
  geom_text(
    aes(label = paste(print.p)),
    vjust = -1.5,
    hjust = 0,
    angle = 45,
    cex = 4,
    parse = T
  ) +
    
  # specify the range of the plot, *1.25 to provide enough space for the p-values
  scale_y_continuous(limits = c(0, max(prs.result$R2) * 1.25)) +
  
  # specify the axis labels
  xlab(expression(italic(P) - value ~ threshold ~ (italic(P)[T]))) +
  ylab(expression(paste("PRS model fit:  ", R ^ 2))) +
  
  # draw a bar plot
  geom_bar(aes(fill = -log10(P)), stat = "identity") +
  
  # specify the colors
  scale_fill_gradient2(
    low = "dodgerblue",
    high = "firebrick",
    mid = "dodgerblue",
    midpoint = 1e-4,
    name = bquote(atop(-log[10] ~ model, italic(P) - value),)
  ) +
  
  # add title
  labs(title=paste(name, "-mdd")) +
  
  # some beautification of the plot
  theme_classic() + theme(
    axis.title = element_text(face = "bold", size = 18),
    axis.text = element_text(size = 14),
    legend.title = element_text(face = "bold", size =18),
    legend.text = element_text(size = 14), axis.text.x = element_text(angle = 45, hjust = 1)
  ))
  
  # save plots - if you want to save to a file, remove the print wrapper around ggplot command and uncomment this line 
#ggsave(paste0("~/Desktop/Broad/tj/prs/plots/", name, "-mdd_glm_bar_plot.png"), height = 7, width = 7)
```


# Plot II - visualise the relationship between the "best-fit" PRS (which may have been obtained from any of the PRS programs) and the phenotype of interest, coloured according to sex
```{r}
# dataset name

name = "gawli"

# read in files
prs <- read.table(paste0("~/Desktop/Broad/tj/prs/batch_outputs/mdd/", name, "/", name, ".0.5.profile"), header=T) # for all 8 samples, 0.5 was the P-value threshold that generated the "best-fit" PRS
pheno <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".pheno"), header=T)
sex <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".cov"), header=T)

# rename the sex
sex$Sex <- as.factor(sex$SEX)
levels(sex$Sex) <- c("Male", "Female")
  
# merge the files
dat <- merge(merge(prs, pheno), sex)

# start plotting
ggplot(dat, aes(x=SCORE, y=PHENOTYPE, color=Sex))+
  geom_point()+
  theme_classic()+
  labs(title=paste(name, "-mdd")) +
  labs(x="Polygenic Score", y="PHENOTYPE")

# uncomment to save to a file 
#ggsave(paste0("~/Desktop/Broad/tj/prs/plots/", name, "_mdd_scatter_plot.png"), height = 7, width = 7)

```

# ##########################################################################

# ##########################################################################

# GCTA plots 

# num of cases and controls per dataset - for GCTA plots annotation purposes 
```{r}
# set working dir 
setwd("~/Desktop/Broad/tj/gcta/fam_files")
# list of fam file names 
fam_files <- c("scz.celso.QC.fam", "scz.cgs1c.QC.fam", "scz.gawli.QC.fam", "scz.xclm2.QC.fam", "scz.xclo3.QC.fam", "scz.xswe1.QC.fam", "scz.xswe5.QC.fam", "scz.xswe6.QC.fam")

# import fam files as a list and add a column to keep track of which file it came from 
myFamData_list <- lapply(fam_files, function(x) {
  out <- data.table::fread(x, header = F)
  out$source_file <- strsplit(x, "\\.")[[1]][2]
  return(out)
})

# merge the list of files into one 
myFamData <- data.table::rbindlist(myFamData_list)

# count the number of cases and controls per dataset and save that as a dataframe
library(janitor)
temp_tbl <- tabyl(myFamData, source_file,  V6)
colnames(temp_tbl) <- c("dataset","controls","cases") # update col names
# set the first column as row names
pheno_count_per_ds <- temp_tbl[,-1] 
rownames(pheno_count_per_ds) <- temp_tbl[,1]

# prep the count df to be added beside plots
my_tbl <- tableGrob(pheno_count_per_ds)
```

# plots 
```{r}
# set working directory  
setwd("~/Desktop/Broad/tj/gcta/outputs")

# list of file names 
files <- c("celso.txt", "cgs1c.txt", "gawli.txt", "xclm2.txt", "xclo3.txt", "xswe5.txt", "xswe6.txt")

# import files as a list and add a column to keep track of which file it came from 
myData_list <- lapply(files, function(x) {
  out <- data.table::fread(x, header = T)
  out$source_file <- tools::file_path_sans_ext(x)
  return(out)
})

# merge the list of files into one 
myData <- data.table::rbindlist(myData_list)

# only select out the rows we are interested in 
subData1 <- myData[grepl("V\\(G\\)\\/Vp\\_L", myData$Source),]

# ########## plot I 

# plot
p1 <- ggplot(subData1, mapping=aes(x=source_file, y=Variance)) + 
  geom_pointrange(aes(ymin=Variance-SE, ymax=Variance+SE)) +
  labs(title="V(G)/Vp_L across samples with SE") 

# final plot with count tbl
grid.arrange(p1, arrangeGrob(my_tbl), ncol = 2)

# save plot 
#ggsave(paste0("~/Desktop/Broad/tj/gcta/ratio_plot.png"), height = 7, width = 7)

# only select out the rows we are interested in 
subData2 <- myData[grepl("V\\(G\\)$", myData$Source),]

 # ########## plot II 

# plot
p2 <- ggplot(subData2, mapping=aes(x=source_file, y=Variance)) + 
  geom_pointrange(aes(ymin=Variance-SE, ymax=Variance+SE)) +
  labs(title="V(G) across samples with SE")

# final plot with count tbl
grid.arrange(p2, arrangeGrob(my_tbl), ncol = 2)

# save plot to a file - uncomment the line below 
#ggsave(paste0("~/Desktop/Broad/tj/gcta/gene_var_plot.png"), height = 7, width = 7)
```

# ##########################################################################

# ##########################################################################

# ADDITIONAL CODE 

# Finding the "best-fit" PRS and plot I (for linear regression)
```{r}
sample_names <- c("celso", "cgs1c", "gawli", "xclm2", "xswe1", "xclo3", "xswe6", "xswe5")
p.threshold <- c(0.001,0.05,0.1,0.2,0.3,0.4,0.5) 

for (name in sample_names){
  phenotype <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".pheno"), header=T)
  pcs <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".eigenvec"), header=F)
  colnames(pcs) <- c("FID", "IID", paste0("PC",1:6))
  covariate <- read.table(paste0("~/Desktop/Broad/tj/prs/generate_qc_files/", name, "/scz.", name, ".cov"), header=T)
  pheno <- merge(merge(phenotype, covariate, by=c("FID", "IID")), pcs, by=c("FID","IID")) 
  null.r2 <- summary(lm(PHENOTYPE~., data=pheno[,!colnames(pheno)%in%c("FID","IID")]))$r.squared 
  prs.result <- NULL 
  for(i in p.threshold){
    pheno.prs <- merge(pheno, read.table(paste0("~/Desktop/Broad/tj/prs/batch_outputs/", name, "/", name, ".", i, ".profile"), header=T)[,c("FID","IID", "SCORE")], by=c("FID", "IID")) 
  	model <- summary(lm(PHENOTYPE~., data=pheno.prs[,!colnames(pheno.prs)%in%c("FID","IID")])) 
  	model.r2 <- model$r.squared 
  	prs.r2 <- model.r2-null.r2 
  	prs.coef <- model$coeff["SCORE",] 
  	prs.result <- rbind(prs.result, data.frame(Threshold=i, R2=prs.r2, P=as.numeric(prs.coef[4]), BETA=as.numeric(prs.coef[1]), SE=as.numeric(prs.coef[2]))) 
  } 
  
  print(prs.result[which.max(prs.result$R2),]) 
  
  # generate a pretty format for p-value output
  prs.result$print.p <- round(prs.result$P, digits = 3)
  prs.result$print.p[!is.na(prs.result$print.p) & prs.result$print.p == 0] <- format(prs.result$P[!is.na(prs.result$print.p) & prs.result$print.p == 0], digits = 2)
  prs.result$print.p <- sub("e", "*x*10^", prs.result$print.p)

# Initialize ggplot, requiring the threshold as the x-axis (use factor so that it is uniformly distributed)
  ggplot(data = prs.result, aes(x = factor(Threshold), y = R2)) +
    # Specify that we want to print p-value on top of the bars
    geom_text(
      aes(label = paste(print.p)),
      vjust = -1.5,
      hjust = 0,
      angle = 45,
      cex = 4,
      parse = T
    ) +
    # Specify the range of the plot, *1.25 to provide enough space for the p-values
    scale_y_continuous(limits = c(0, max(prs.result$R2) * 1.25)) +
    # Specify the axis labels
    xlab(expression(italic(P) - value ~ threshold ~ (italic(P)[T]))) +
    ylab(expression(paste("PRS model fit:  ", R ^ 2))) +
    # Draw a bar plot
    geom_bar(aes(fill = -log10(P)), stat = "identity") +
    # Specify the colors
    scale_fill_gradient2(
      low = "dodgerblue",
      high = "firebrick",
      mid = "dodgerblue",
      midpoint = 1e-4,
      name = bquote(atop(-log[10] ~ model, italic(P) - value),)
    ) +
    # add title
    labs(title=name) +
    # Some beautification of the plot
    theme_classic() + theme(
      axis.title = element_text(face = "bold", size = 18),
      axis.text = element_text(size = 14),
      legend.title = element_text(face = "bold", size =18),
      legend.text = element_text(size = 14), axis.text.x = element_text(angle = 45, hjust = 1)
    )
  
  # save plots
  #ggsave(paste0("~/Desktop/Broad/tj/prs/plots/", name, "_lm_bar_plot.png"), height = 7, width = 7)
}
```

# ##########################################################################

# JUNK CODE

# import PRS files 
```{r}
# first file - bg
mydir_bg <- "batch_outputs/output/bg" # set directory path 
myfiles_bg <- list.files(path=mydir_bg, pattern="*.profile", full.names=TRUE) # set paths for each file
content_bg <- myfiles_bg %>% lapply(read.table, header = T) # # read content of each file as large list 
filename_bg <- myfiles_bg %>% basename() %>% as.list() # file names as list 
prs_lists_bg <- mapply(c, content_bg, filename_bg, SIMPLIFY = FALSE) # combine file content list and file name list
prs_bg <- rbindlist(prs_lists_bg, fill = T) # unlist all lists # change column name
names(prs_bg)[7] <- "which_threshold?"

# second file - bgs
mydir_bgs <- "batch_outputs/output/bgs" # set directory path 
myfiles_bgs <- list.files(path=mydir_bgs, pattern="*.profile", full.names=TRUE) # set paths for each file
content_bgs <- myfiles_bgs %>% lapply(read.table, header = T) # # read content of each file as large list 
filename_bgs <- myfiles_bgs %>% basename() %>% as.list() # file names as list 
prs_lists_bgs <- mapply(c, content_bgs, filename_bgs, SIMPLIFY = FALSE) # combine file content list and file name list
prs_bgs <- rbindlist(prs_lists_bgs, fill = T) # unlist all lists # change column name
names(prs_bgs)[7] <- "which_threshold?"
```

# plot
```{r}
ggplot(prs_bg, aes(x=`which_threshold?`, y=SCORE, fill=PHENO)) + geom_boxplot()
ggplot(prs_bgs, aes(x=`which_threshold?`, y=SCORE, fill(PHENO))) + geom_boxplot()
```

# interactive plot 
```{r}
plot_bg <- ggplot(prs_bg, aes(x=`which_threshold?`, y=SCORE, color=PHENO)) + geom_boxplot()
ggplotly(plot_bg) 
plot_bgs <- ggplot(prs_bgs, aes(x=`which_threshold?`, y=SCORE, color=PHENO)) + geom_boxplot()
ggplotly(plot_bgs) 
```



